\documentclass{report}

% match packages
\usepackage{amsmath}
\usepackage{xfrac}
\usepackage{breqn}  %line breaking for equations

% \usepackage{enumerate}
\usepackage{fixltx2e}
\usepackage[shortlabels]{enumitem}
% \setlist{nosep} #no separation space between enumerate items

% \usepackage[left=1.5in, right=1in, top=1in, bottom=1in, includefoot, headheight=13.6pt]{geometry}
\usepackage{parskip} %no indention, looks better

\usepackage{xcolor}
\usepackage{sectsty}
% \chapterfont{\color{cyan}}  % sets color of chapters
% \sectionfont{\color{cyan}\LARGE}  % sets color and font of sections
% \subsectionfont{\color{cyan}}
% \subsubsectionfont{\color{cyan}}
% \paragraphfont{\color{cyan}}


% Package and setting for including pictures
\usepackage{graphicx}
\graphicspath{ {./Image/} }
\usepackage[font={small,it}]{caption} % Why arguments? because caption and content look alike and therefore, they look like shit
\usepackage{subcaption}


% Packages for tables
\usepackage{tabularx}	%limiting table width
\usepackage{multirow}
\usepackage{booktabs}

% Package and Settings for table of contents
% Hyperlink Settings
\usepackage{hyperref}
\hypersetup{colorlinks, citecolor=black, filecolor=black, linkcolor=black, urlcolor=black}
% Settings for depth of table of contents
\setcounter{tocdepth}{3}
\setcounter{secnumdepth}{3}

%Package for creating appendix
\usepackage[toc,page]{appendix}

% Packages for citing and reference
\usepackage[numbers]{natbib}

% Packages for plotting
\usepackage{pgfplots}
\pgfplotsset{compat=1.8}
\usepgfplotslibrary{fillbetween}  
\usetikzlibrary{graphs} 
\usepackage{tikz}
% some tikz style defining
\usetikzlibrary{arrows,positioning} 
\tikzset{
    %Define standard arrow tip
    >=stealth',
    %Define style for boxes
    punkt/.style={
           rectangle,
           rounded corners,
           draw=black, very thick,
           text width=3.37cm,
           minimum height=2em,
           text centered},
    % Define arrow style
    pil/.style={
           ->,
           thick,
           shorten <=2pt,
           shorten >=2pt,}
}


% Packages for including code lines
\usepackage{listings}

% Define command for keyword in abstract
\providecommand{\keywords}[1]{\textbf{\textit{Keywords:---}} #1}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%            Begin Document              %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\include{titlepage}

\begin{abstract}


Dynamics of railway bridges is a complicated problem that normally needs numerical simulation to conduct researches on. However, this thesis takes advantage of the numerical results provided in previous researches and based on these researches, further conclusions are made by using them in simplified model. 

Recently long span railway bridges being designed in the Netherlands are being rejected by a particular Eurocode criterion that requires bridges to possess a first lateral natural frequency higher than $1.2Hz$. Due to the fact that generally bridge's first lateral natural frequency decreases as the span increases, it can be seen that $1.2Hz$ criterion is rejecting almost all bridge with a span longer than 150m. 

This report succeeds in pursuing the original documents of $1.2Hz$ criterion and the knowledge in the documents initiates further researches on the lateral dynamics of railway bridges. Besides $1.2Hz$ criterion itself, following topics are researched with the information provided by previous researches:

\begin{enumerate}
    \item Train-bridge lateral resonance mechanisms, including axle repeat pattern resonance and kinematic movement resonance,
    \item Lateral force on tracks caused by the operation of railway vehicle and key parameters influencing the force.
    % \item Lateral wavelength of trains running in the Netherlands, including axle repeat pattern wavelength and kinematic movement wavelength
\end{enumerate}
    
Taking advantage of the items above, a simplified model for checking the lateral railway bridge dynamics is developed to quantify the lateral dynamic resonance response of railway bridge under horizontal dynamic vehicle load. This method aims to serve for engineering purposes and provide an alternative way of verifying railway bridge lateral dynamics. The practical method is developed by an analytical approach, based on the numerical simulation results provided by other researches.

An illustration of the usage of the practical method is conducted on the basis of a real bridge project. The method is also implemented in Matlab scripts to automate the checking procedure.


\vspace*{1cm}

\keywords{Eurocode, railway bridge dynamics, lateral dynamics, rail dynamics, analytical solution, 1.2Hz criterion, train wavelength, nosing force, lateral force on track}

\end{abstract}




\chapter*{Acknowledgments}

Hereby I would like to express my deepest appreciation to all those who helped me in completing this thesis and my engineering studies.

First of all, I would like to thank to Matthijs van Almen, my daily supervisor at Iv-Infra, for his patient guidance during the entire thesis process. His guidance is like the light that helps me finding the right path in the darkness. Nevertheless, his way of thinking also enlightened me. I would never have completed the thesis without his help. 

I also want to express my appreciation to Prof. Frans Bijaard, Ir. Roland Abspoel, Dr. Micha{\"e}l Steenbergen, Prof. Rolf Dollevoet,  the members of the thesis committee from Delft University of Technology. Their professional knowledge and general interest in the topic were valuable assets to my work.

Special thanks to Michel Koop, who provided me with the opportunity to carry out this research at Iv-Infra, to Charalampos Bouras, who was always eager to provide help whenever I needed, and to all the colleagues at the steel department of Iv-Infra, who provided me a friendly atmosphere.

I really appreciate the help of Ron van der Zwan and the access to ERRI D181 research resources he provided. I also appreciate Paul Vos, Jean-Jacques Reber sharing their background information of D181 committee. Same appreciation goes to Alan Minnis from DeltaRail for providing the information of D181 DT329 researches.

I am deeply grateful to my parents, Guolin Deng and Jiafen Wang, who always believed in me and were supporting my studies in The Netherlands. 

Last but not least, I am thankful to all my friends in Delft, who gave me many unforgettable memories during my studies.

\vspace*{1cm}

Sijian Deng

Delft,  \today


\tableofcontents
\listoffigures
\listoftables

\include{introduction}

\include{c1}

\include{c2}

\include{c3}

\include{c4}

\include{c5}

\include{c6}

\include{c7}

% \include{firstSegment}

% \include{secondSegment}

\include{thirdSegment}

\bibliography{ref} 
\bibliographystyle{plainnat}
\end{document}